---
title: "Lab 2"
author: "Meredith Tucker"
date: "2/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
head(choco)

```

# Question Set (Individual)

1. How are the ratings distributed? Draw a histogram of the ratings and describe it. Don’t forget to mention outliers, if there are any.

```{r}
Rate <- choco$Rating
hist(Rate, main="Distribution of Ratings", xlab="Rating")
```


The most frequent Rating in the data set are ratings between 3 and 3.5. The second most frequent rating are those between 2.5 and 3. There are very few values that have a rating of 1 or a rating of 5. 



2. Do ratings depend on the cacao percentage of a chocolate bar?

```{r}
plot(choco$Cocoa.Pct, choco$Rating, main="Cacao Percentage and Ranking", xlab='Cacao Percentage', ylab='Rating')
```

There is no clear correlation shown in the scatterplot between the percenatage of cacao and the rating of the chocolate. 

