---
title: "Lab 2 Team"
author: "Meredith Tucker, Mike Zaino"
date: "2/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. What is the overall number of chocolate bars rated?

```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
head(choco)
```

```{r}
length(choco$Rating)
```

There are 1852 chocolate bars that are rated in the data set. 


2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.

```{r}

choco$Review.Date <- as.factor(choco$Review.Date)


YearTotal <- c(72, 77,93,123,111,165, 195,184, 247,285,219,81)

YearNames <- c("2006", "2007", "2008", "2009", '2010', '2011', '2012', '2013', '2014', '2015', '2016', '2017')

barplot(YearTotal,names.arg = YearNames)


```

3. Which are the three locations with the most ratings? How do ratings compare across these company locations?

```{r}

loco <- choco$Company.Location
names(loco) <- choco$Company.Location
numloco <- summary(loco)
biggest3 <- sort(numloco, decreasing = TRUE)[1:3]
biggest3

USA <- choco[choco$Company.Location == "U.S.A.", ]
France <- choco[choco$Company.Location == "France", ]
Canada <- choco[choco$Company.Location == "Canada", ]

table <- c(mean(USA$Rating),mean(France$Rating),mean(Canada$Rating))
names(table) <- c("USA","France", "Canada")
table
```

The three countries that have the most number of ratings all have about the same average rating. Canada has the highest rating with approximently 3.31. Then France with 3.25, and then USA with 3.16.

4. Brainstorm and write down an interesting question that can be answer from the dataset. The question should not duplicate the questions above.

Question; Which company has the most number of ratings?

5. Answer the question from the dataset.

```{r}
head(sort(summary(choco$Company), decreasing=T))

```

Without including the unnamed companies, the largest company reviewed was Soma.

6. Write one Paragraph commenting on the workflow

We worked dilgently together and used our resources to find the best methods to create solutions. When we started a new problem we brainstormed ideas of what to do. From there we both worked on our brainstorming ideas each on our laptops and then combined the end product. If it would not work, we then used trial and error to fix the mistake. 
